---
title: "My Fancy Presentation"
author: "Mao Soldevilla"
date: "2/11/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
Some content

## My title

### A top level subheading

- Bullet one
- Bullet two

#### A Second level subheading
1. Item a
2. Item b

## My new slide

Plain text

*italicided text*

**Bold text**

`for (i %in% 1:10)`

## New silde

```{r, comment = "", echo=TRUE, eval = FALSE, }
head(mtcars)
```

## New silde 1

```{r, comment = "", echo=TRUE}
head(mtcars)
```

## New silde 2

```{r, echo=FALSE, fig.align='center'}
plot(mtcars$wt, mtcars$mpg, xlab ="weight", ylab = "MPG")
```


***
A Slide without a tittle

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

